---
title: 
author:
- name: '**Emadeldin Hassanin**'
  affil: 1
  main: yes
  twitter: emad_hassanin
  email: hassanin@uni-bonn.de
- name: R. Aldisi
  affil: 1
- name: DR Bobbili
  affil: 2
- name: P. May
  affil: 2
- name: P. Krawitz
  affil: 1
- name: C. Maj
  affil: 1
main_topsize: 0.2
column_numbers: 2
output:
  posterdown::posterdown_betterport:
    self_contained: no
    pandoc_args: --mathjax
    number_sections: no
affiliation:
- num: 1
  address: Institute of Genomic Statistics and Bioinformatics, University of Bonn,
    Bonn, Germany
- num: 2
  address: Bioinformatics Core, Luxembourg Centre for Systems Biomedicine (LCSB),
    Belvaux, Luxembourg
main_findings: '**P19.045.D**  <br> **Early-onset prostate cancer** : Interplay of PRS & family history and rare pathogenic variants'
author_textsize:	"1.5em"
affiliation_textsize:	"35px"
geometry: "left=3cm,right=3cm,top=2cm,bottom=2cm"
logoleft_name: Figures/IGSBlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
main_bottomsize: 0.1
bibliography: ref.bib
link-citations: yes
---

<!-- poster_height: "59in" -->

<!-- poster_width: "35in" -->

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

```{=html}
<style>
#main-img-left {
 width: 30%;
 vertical-align: middle;
}
#main-img-center {
 width: 10%;
}
#main-img-right {
 width: 10%;
 vertical-align: middle;
}
</style>
```
# Introduction

1.  Polygenic risk score (PRS) has been known to influence development of the prostate cancer over a life course.

2.  PRS have recently been shown to have relative risks that depend on age, and genetic relative risks decrease with increasing age.

3.  A recent study assessed the interplay of polygenic risk, rare pathogenic variants, and family history [@pmid34906469].

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

We aimed to comprehensively assess the role of polygenic risk score (PRS):

-   in the early-onset prostate cancer (PC) vs late-onset

-   in the absence or presence of a family history of PC (FH)

-   in the absence or presence of rare pathogenic variants (PV, across 5 PC susceptibility genes - HOXB13, BRCA2, ATM, CHEK2, BRCA1).

# Methods


# References
